### 2018-12-07 Paper_HTML/Paper_HTML.Rmd
update shiny_portal
new graphs

# opts_knit$set(root.dir = "C:\\Users\\Pedro Albuquerque\\Desktop\\AutomationJobs")
opts_knit$set(root.dir = "C:/Users/rafal/Google Drive/LAMFO/AutomationJobs")

@@

```{r fig3, fig.cap=fig$cap("fig3", "Série temporal da ocupação por nível de automação."), message=FALSE, warning=FALSE}
library(tidyverse)
library(scales)
profile<-read.csv2("Data/Occupation Structure/CBO2002 - PerfilOcupacional.csv")
profile<-data.frame("cbo2002"=unique(profile[,5]))
#Read the results
results<-readRDS("shiny_portal/ProbabilityBayes.rds")
forecast<-read.csv("shiny_portal/Previsao.csv")

@@

#Calculate the total
total.cbo <- forecast %>% 
              group_by(cbo2002, ano) %>% 
              summarise(Total=sum(empregados))

@@

```{r save}
saveRDS(a, "Box_Paper.RDS")
saveRDS(g, "Serie_Paper.RDS")
saveRDS(g2, "Serie_Paper2.RDS")
```

>>>>

# opts_knit$set(root.dir = "C:\\Users\\Pedro Albuquerque\\Desktop\\AutomationJobs")
opts_knit$set(root.dir = "C:/Users/B2657804/Google Drive/LAMFO/AutomationJobs")

@@

```{r fig3, fig.cap=fig$cap("fig3", "Série temporal da ocupação por nível de automação."), message=FALSE, warning=FALSE}
library(tidyverse)
library(scales)
profile<-read.csv2("Data/Occupation Structure/CBO2002 - PerfilOcupacional.csv")
profile<-data.frame("cbo2002"=unique(profile[,5]))
#Read the results
results<-readRDS("Analysis/ProbabilityGP_round.rds")
forecast<-read.csv("shiny_portal/Previsao.csv")

@@

#Calculate the total
total.cbo <- forecast %>% 
  mutate(cbo2002 = factor(cbo2002)) %>% 
  group_by(cbo2002, ano) %>% 
  summarise(Total=sum(empregados))

@@

```{r save}
saveRDS(Comp, "Box_Paper.RDS")
saveRDS(g, "Serie_Paper.RDS")
saveRDS(g2, "Serie_Paper2.RDS")
```
